### 2016-01-18 paper.tex
Call turbine a physical model and note that the measurements were experimental; resolves #49

The mechanical power, total rotor drag, and near-wake flow of a 1:6 scale
Reference Model 2 (RM2) vertical-axis cross-flow turbine were measured in a
towing tank. Performance was measured at multiple Reynolds numbers by varying
tow carriage speed, and weak linear $Re$-dependence was achieved at a turbine
diameter Reynolds number $Re_D \approx 10^6$. An optimal tip speed ratio
$\lambda_0 = 3.1$ was chosen, at which the near wake velocity was measured at 1
m $(x/D=0.93)$ downstream. Mean velocity, turbulence, and mean kinetic energy
transport mechanisms were compared and contrasted with results from a high
solidity turbine acquired with the same test apparatus. Overall, lower levels of
streamwise wake recovery were calculated for the RM2 rotor---a consequence of
both the relatively low solidity and tapered blades. The effects of blade
support strut drag on turbine performance were investigated by covering the
rotor's NACA 0021 struts with cylinders. As expected, this modification
drastically reduced rotor power coefficient. Strut drag was also measured for
the NACA 0021 and cylindrical configurations with the blades removed. These
measurements provide a comprehensive open dataset for validating numerical
models' predictive capabilities for low solidity rotors.

@@

A 1:6 scale model of the RM2 rotor was designed and fabricated. Turbine
geometric parameters were scaled from the RM2 design report \cite{Barone2011},
with the exception of the shaft diameter, which was scaled from the SAFL RM2
model \cite{Hill2014}. The hubs were designed to be similar to the SAFL model,
which may aid in comparison of the results, though this was not a top priority.
Geometric parameters are shown in Tab.~\ref{tab:turb-geom} and a drawing of the
turbine design is shown in Fig.~\ref{fig:turbine-drawing}. The turbine model
components---blades, struts, shaft, and center hub sections---were fabricated
from 6061-T6 aluminum, which was hardcoat anodized per MIL-8625-A, type III,
class 2 specifications. CAD models of the turbine are available from
\cite{Bachant2015-RM2-CAD}.

>>>>

The mechanical power, total rotor drag, and near-wake flow of a 1:6 scale
Reference Model 2 (RM2) vertical-axis cross-flow turbine were measured
experimentally in a towing tank. Performance was measured at multiple Reynolds
numbers by varying tow carriage speed, and weak linear $Re$-dependence was
achieved at a turbine diameter Reynolds number $Re_D \approx 10^6$. An optimal
tip speed ratio $\lambda_0 = 3.1$ was chosen, at which the near wake velocity
was measured at 1 m $(x/D=0.93)$ downstream. Mean velocity, turbulence, and mean
kinetic energy transport mechanisms were compared and contrasted with results
from a high solidity turbine acquired with the same test apparatus. Overall,
lower levels of streamwise wake recovery were calculated for the RM2 rotor---a
consequence of both the relatively low solidity and tapered blades. The effects
of blade support strut drag on turbine performance were investigated by covering
the rotor's NACA 0021 struts with cylinders. As expected, this modification
drastically reduced rotor power coefficient. Strut drag was also measured for
the NACA 0021 and cylindrical configurations with the blades removed. These
measurements provide a comprehensive open dataset for validating numerical
models' predictive capabilities for low solidity rotors.

@@

A 1:6 scale physical model of the RM2 rotor was designed and fabricated. Turbine
geometric parameters were scaled from the RM2 design report \cite{Barone2011},
with the exception of the shaft diameter, which was scaled from the SAFL RM2
model \cite{Hill2014}. The hubs were designed to be similar to the SAFL model,
which may aid in comparison of the results, though this was not a top priority.
Geometric parameters are shown in Tab.~\ref{tab:turb-geom} and a drawing of the
turbine design is shown in Fig.~\ref{fig:turbine-drawing}. The turbine model
components---blades, struts, shaft, and center hub sections---were fabricated
from 6061-T6 aluminum, which was hardcoat anodized per MIL-8625-A, type III,
class 2 specifications. CAD models of the turbine are available from
\cite{Bachant2015-RM2-CAD}.
